### 2018-07-05 Thesis/Parts/Data/Data.tex
updates

The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the Figures as \textbf{embedding}.

@@

The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word. We will refer to this embedding in the Figures as \textbf{tfidf\_embedding}.

@@

The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance. We will refer to this embedding in the Figures as the \textbf{10k\_embedding}.

@@

The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise. We will refer to this embedding in the Figures as \textbf{5k\_embedding}.

@@

The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set. We will refer to this embedding in the Figures as \textbf{1k\_6k\_embedding}. We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.

@@

We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation. This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K". We will refer to the TF-IDF configurations in our Figures as "tfidf\_vocabulary size\_hash bucket size".

@@

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

@@

The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data. \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark. This allows for much tighter integration between relational and procedural processing. The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\

@@

To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\

@@

The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line. The median rank therefore indicates the position of the "normal/typical"  article. This median rank differs from the average, since the median is not influenced by a single value. If the median is 20, it does not matter if an article is 25 of 250, it does matter however if an articles is 19 or 21. For the average this is not the case, the average is influenced by single articles. Therefore it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of the articles in our validation set. We also calculate the average score for the title and abstract of all articles. This gives us four scores: median title rank, median abstract rank, average title rank \& average abstract rank.\\

>>>>

The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as \textbf{embedding}.

@@

The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word. We will refer to this embedding in the figures as \textbf{tfidf\_embedding}.

@@

The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance. We will refer to this embedding in the figures as the \textbf{10k\_embedding}.

@@

The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise. We will refer to this embedding in the figures as \textbf{5k\_embedding}.

@@

The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set. We will refer to this embedding in the figures as \textbf{1k\_6k\_embedding}. We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.

@@

We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation. This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K". We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".

@@

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

@@

The research has been done in a python-databricks environment, which used Spark, a library that offers tools to work with big-data. \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark. This allows for much tighter integration between relational and procedural processing. The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\

@@

To calculate the distance between two vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\

@@

The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line. The median rank therefore indicates the position of the "normal/typical"  article. This median rank differs from the average, since the median is not influenced by a single value. If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an articles is 19 or 21. For the average this is not the case, the average is influenced by single articles. Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of the articles in our validation set. We also calculate the average score for the title and abstract of all articles. This gives us four scores: \textbf{median title rank, median abstract rank, average title rank \& average abstract rank.}\\
